---
title: Building a blogdown publication list from bibtex file (updated)
author: Tormod Bøe
date: '2019-30-12'
slug: building-a-blogdown-publication-list-from-bibtex-file
categories:
  - blogdown
  - R
  - rmarkdown
  - bibtex
tags: []
draft: no
---

The best way to do this now is to follow the guide on the following [page](https://sourcethemes.com/academic/docs/managing-content/#create-a-publication).


I tried to build markdown files to use for publication section of my blog programmatically using r. I came close, but not all the way there. 

The following code takes a bibtex file, reads it into r, formats the output and splits each citation out to a separate markdown file. Unfortunately, there were som spaces and formatting errors that I was not able to get rid of, so I had to go through some manual cleaning up afterwards.

The goal was to get pretty close to this yaml result, as I am using the setup from Rob Hyndman's excellent site, which he has shared on github. 

```{r, eval = F}
---
author: Rob&nbsp;J&nbsp;Hyndman, Shu Fan
comments: false
date: 2014-05-22 01:46:18+00:00
slug: mefm
title: Monash Electricity Forecasting Model
wordpress_id: 2452
kind:
  unpublished
tags:
  - electricity
- forecasting
file: MEFMR1.pdf
---
```

```{r, eval = F}
devtools::install_github("ottlngr/bib2df")
library(bib2df)
bib <- bib2df("/.../bibtex_file.bib", separate_names = F)
```

```{r, eval = F}
yamllist <- list()
for (i in 1:nrow(bib)) { 
  au <- paste0("author: ", paste(bib$AUTHOR[[i]], collapse =", "))
  co <- paste0("comments: false")
  yr <- paste0("date: '", paste(bib$YEAR[[i]]),"'")
  date <- paste0(bib$YEAR[[i]])
  slu <- paste0("slug: ", paste(bib$BIBTEXKEY[[i]]))
  tit <- paste0("title: ", paste(bib$TITLE[[i]]))
  pub <- paste("kind:", "  published", sep = "\n")
  name <- paste0("article", i, sep = '')
  # abst <- paste0(bib$ABSTRACT[[i]])
  tmp <- list(au=au, co =co, yr=yr,slu=slu, tit=tit , pub=pub)
  yamllist[[name]] <- tmp
}
```

I did this two times, the second time adding some extra fields... 

```{r, eval = F}
yamllist2 <- list()
for (i in 1:nrow(bib)) { 
  au <- paste0("author: ", paste(bib$AUTHOR[[i]], collapse =", "))
  co <- paste0("comments: false")
  yr <- paste0("date: '", paste(bib$YEAR[[i]]),"'")
  date <- paste0(bib$YEAR[[i]])
  slu <- paste0("slug: ", paste(bib$BIBTEXKEY[[i]]))
  tit <- paste0("title: ", paste(bib$TITLE[[i]]))
  pub <- paste("kind:", "  published", sep = "\n")
  name <- paste0("article", i, sep = '')
  abst <- paste0(bib$ABSTRACT[[i]])
  tmp2 <- list(au=au, co =co, yr=yr,slu=slu, tit=tit , pub=pub, abst = abst, date = date)
  yamllist2[[name]] <- tmp2
}
```

This loop prints out the markdown files into the `publications` folder in my `blogdown` project.

```{r, eval = F}
for (i in 1:length(yamllist)) {
  cat(paste0("---", sep = "\n"),
      paste0(unlist(yamllist[i]), sep = "\n"), 
      paste0("---", sep = "\n"), 
      paste0("\n", yamllist2[[i]]$abst, sep = "\n"), file = paste0("content/publications/", yamllist2[[i]]$date, "-01-01-", names(yamllist)[i], ".md"))
}
```

Unfortunately, I was not able to get rid of the spacing before the final "---" in the YAML output, nor the spacings before the yaml fields title, author etc. I had to reopen the files in atom - for ease - and did a manual removal there. For files that did not work directly, I also used the "Update Metadata" adding from `bookdown`. Took a while, but still a lot less than manually copying and pasting this information from the web or reference manager would have done. 






