---
title: SDQ Predictive algoritm in R
author: Tormod Bøe
date: '2020-02-13'
slug: sdq-predictive-algoritm-in-r
categories:
  - R
  - SDQ
  - screening
tags:
  - r
  - sdq
subtitle: ''
summary: ''
authors: []
lastmod: '2020-02-13T20:43:30+01:00'
featured: no
draft: no
image:
  caption: ''
  focal_point: ''
  preview_only: no
projects: []
---

> Adapted from syntax available at the [SDQ website](http://www.sdqinfo.com/c4.html).   

## The predictive algorithm is based on up to twelve input variables:

__phyper__ 	=	SDQ hyperactivity score from parent SDQ  
__thyper__ 	=	SDQ hyperactivity score from teacher SDQ  
__shyper__ 	=	SDQ hyperactivity score from self-report SDQ  
__pconduct__ 	=	SDQ conduct problems score from parent SDQ  
__tconduct__ 	=	SDQ conduct problems score from teacher SDQ  
__sconduct__ 	=	SDQ conduct problems score from self-report SDQ  
__pemotion__ 	=	SDQ emotional symptoms score from parent SDQ  
__temotion__ 	=	SDQ emotional symptoms score from teacher SDQ  
__semotion__ 	=	SDQ emotional symptoms score from self-report SDQ  
__pimpact__ 	=	SDQ impact score from parent SDQ  
__timpact__ 	=	SDQ impact score from teacher SDQ  
__simpact__ 	=	SDQ impact score from self-report SDQ  

The algorithm generates four output variables:  
__sdqed__ 	=	prediction of an emotional disorder  
(0 = unlikely, 1 = possible, 2 = probable)  
__sdqcd__ 	=	prediction of a conduct disorder  
(0 = unlikely, 1 = possible, 2 = probable)  
__sdqhk__ 	=	prediction of a hyperactivity disorder  
(0 = unlikely, 1 = possible, 2 = probable)  
__anydiag__	=	prediction of any psychiatric disorder  
(0 = unlikely, 1 = possible, 2 = probable)  

----

```{r setup, include = FALSE}
# Set-up
knitr::opts_chunk$set(tidy = FALSE, echo = TRUE, eval = FALSE)
```

### Load required libraries

Note that the current scoring syntax is based on `dplyr`[^1] which must be installed. I also recommend installing `haven`[^2] to read SPSS files into `R`. Use the links to read more about [dplyr](https://dplyr.tidyverse.org/) and [haven](https://haven.tidyverse.org/).

[^1]: `install.packages("dplyr")`
[^2]: `install.packages("haven")`

```{r}
library(dplyr)
library(haven)
```

### Load your data into R

The syntax is based on you reading you data into an object named `sdq`. This could be done with the command: 

```{r}
sdq <- read_sav("sdq.sav")
```

Note that `read_sav` is from `haven` and will fail if you have not installed it. Alternatively, you could use the package [`foreign`](https://cran.r-project.org/web/packages/foreign/foreign.pdf), but this code is only tested with `haven`. 

### SDQ HYPERACTIVITY PREDICTION

```{r}
sdq <- sdq %>%
  mutate(
    phk = case_when(
      phyper>=7 & pimpact>=2 ~ 2,
      phyper>=9 & pimpact>=1 ~ 2,
      phyper>=6 & pimpact>=1 ~ 1,
      phyper>=0 & pimpact>=0 ~ 0)
    )
 
sdq <- sdq %>% 
  mutate(
  shk = case_when(
    shyper>=7 & simpact>=2 ~ 2,
    shyper>=6 & simpact>=1 ~ 1,
    shyper>=0 & simpact>=0 ~ 0)
  )

sdq <- sdq %>% 
  mutate(
    thk = case_when(
      thyper>=7 & timpact>=2 ~ 2,
      thyper>=6 & timpact>=1 ~ 1,
      thyper>=0 & timpact>=0 ~ 0))
    

sdq$pshk <- sdq$phk
sdq$pshk <- ifelse(is.na(sdq$phk), sdq$shk, sdq$pshk)

sdq <- sdq %>% 
  mutate(
  sdqhk = case_when(
    pshk==2 & thk>=1 ~ 2,
    pshk>=1 & thk>=1 ~ 1,
    is.na(pshk) & thk>=1 ~ 1,
    pshk>=1 & !is.na(pshk) & is.na(thk) ~ 1,
    pshk==2 | thk==2 ~ 1,
    phk>=0 | shk>=0 | thk>=0 ~ 0)
  )
```

### SDQ CONDUCT PREDICTION

```{r}
sdq <- sdq %>% 
  mutate(
    sdqcd = case_when(
      is.na(pimpact) & is.na(timpact) & is.na(simpact) ~ NA_real_,
      pconduct>=5 & pimpact>=2 ~ 2,
      tconduct>=4 & timpact>=2 ~ 2,
      sconduct>=6 & simpact>=2 ~ 2,
      pconduct>=4 | tconduct>=3 | sconduct>=5 ~ 1,
      pconduct>=0 | tconduct>=0 | sconduct>=0 ~ 0)
    )
```

### SDQ EMOTION PREDICTION

```{r}
sdq <-  sdq %>% 
  mutate(
    sdqed = case_when(
      semotion>=6 & simpact>=1 ~ 1, 
      pemotion>=5 & pimpact>=1 ~ 1,
      temotion>=5 & timpact>=1 ~ 1, 
      pemotion>=0 | temotion>=0 | semotion>=0 ~ 0)
    )

sdq <- sdq %>% 
  mutate(pem = case_when(
         pemotion>=6 & pimpact>=2 ~ 1,
         TRUE ~ 0))

sdq <- sdq %>% 
  mutate(tem = case_when(
         temotion>=6 & timpact>=2 ~ 1,
         TRUE ~ 0))

sdq <- sdq %>% 
  mutate(sem = case_when(
         semotion>=7 & simpact>=2 ~ 1,
         TRUE ~ 0))

sdq <- sdq %>% 
  mutate(allem = pem + tem + sem)

sdq <- sdq %>% 
  mutate(
    sdqed_tmp = case_when(
      is.na(sdqcd) & is.na(sdqhk) ~ NA_real_,
      allem==1 & (sdqcd==2 | sdqhk==2) ~ 1,
      allem>=1 ~ 2, 
      sdqed==1 ~ 1,
      TRUE ~ 0))

sdq <- sdq %>% 
  mutate(
    sdqed = sdqed_tmp)
```

### SDQ ANY DISORDER PREDICTION

```{r}
sdq <- sdq %>% 
  mutate(
    anydiag = case_when(
      sdqed==2 | sdqcd==2 | sdqhk==2 ~ 2,
      sdqed>=1 | sdqcd>=1 | sdqhk>=1 ~ 1,
      sdqed>=0 | sdqcd>=0 | sdqhk>=0 ~ 0)
  )
```

### CLEANING UP

```{r}
# DELETE MIDWAY VARIABLES
sdq <- sdq %>% select(-phk, -shk, -thk, -pshk, -pem, -tem, -sem, -allem, -sdqed_tmp)

# ASSIGN LABELS
sdq$sdqhk   <- ordered(sdq$sdqhk,   levels = c(0, 1, 2), 
                       labels = c("Unlikely", "Possible", "Probable"))
sdq$sdqcd   <- ordered(sdq$sdqcd,   levels = c(0, 1, 2), 
                       labels = c("Unlikely", "Possible", "Probable"))
sdq$sdqed   <- ordered(sdq$sdqed,   levels = c(0, 1, 2), 
                       labels = c("Unlikely", "Possible", "Probable"))
sdq$anydiag <- ordered(sdq$anydiag, levels = c(0, 1, 2), 
                       labels = c("Unlikely", "Possible", "Probable"))
```

[Download `R` script](https://tormodboe.netlify.com/files/sdq-algorithm.R).