---
title: Generating a random order for students to select their internships (or anything really)
subtitle: 'By automatically retrieving the list of students from Canvas'
author: Tormod
date: '2020-07-29'
slug: generating-random-numbers-for-a-list-of-students-from-canvas
categories:
  - R
  - rcanvas
  - canvas
tags:
  - r
  - rcanvas
  - mitt.uib.no
summary: ''
authors: []
lastmod: '2020-07-29T22:08:16+02:00'
featured: no
image:
  caption: ''
  focal_point: ''
  preview_only: no
projects: []
---

# R script to generate random numbers merged with a list of student names retrieved from Canvas

My students have to choose where they want to have their internship in societal psychology. Since some internships seems to be more popular, I make a random list of numbers from `1:number of students` which I then merge with the list of student names retrieved from Canvas. This then becomes the order in which the students select their internships. 

Since I do this twice per semester every year, I made this (highly overengineered) solution using R. 

```{r, eval=FALSE}
# Load libraries
require(tidyverse) # For data management
require(rcanvas)   # To connect to Canvas
require(openxlsx)  # To output to MS Excel
require(readr)     # To output to csv
```

## Get userinfo for specific course

You will need to input the id for the specific course you want to retrieve student info from. I have added a `YOURID` placeholder to indicate where this has to be entered. See my previous post for how to retrieve all your Canvas courses, and for how to search that list for a specific course. You will also have to add your Canvas access token and the correct server before you can continue. This was described in my previous post.  

The `rcanvas::get_course_items()` functions has options to get only the students, but in my case this does not retrieve their email addresses. I therefore retrive all users in the course, then the students, and then merge the email address with the students names using `dplyr::inner_join()`. 

If you require it, you also have a simple way of making a list with the same information for teachers using a `dplyr::anti_join()`.

```{r, eval=FALSE}
# Get info for all users Canvas
list_of_users <- get_course_items(
  course_id = YOURID, item = "users", include = "email"
  )      

# Get only students, but no email so we must merge 
list_of_students <- get_course_items(
  course_id = YOURID, item = "students", include = "email"
  ) 

# Merge in the email adress
students_with_email <- dplyr::inner_join(list_of_students, 
                                         select(list_of_users, login_id, email), 
                                         by = "login_id", copy = F
                                         )  
# Need a list of teachers as well?
# teachers_with_email <- dplyr::anti_join(
#   list_of_users, list_of_students, by = "id"
#   )
```

## Generate the random numbers 

```{r, eval=FALSE}
# Generate a random number from 1:the number of students
draw_order <- sample(1: length(students_with_email$name), length(students_with_email$name)) 

# Merge the random string of numbers with the dataframe containing student info
students_with_email_number <- cbind(students_with_email, draw_order) 

# Order the lsit of students by their placement in the draw
students_with_email_number <- students_with_email_number %>% arrange(draw_order)  
```

## Save the resulting data frame to Excel and csv.

Since I will publish this list back to Canvas, I only retain the name of the students and their placement in the draw in the files that I store. I use `dplyr::select()` to keep only these two variables.

```{r, eval=FALSE}
# as xls
students_with_email_number %>% 
  select(name, draw_order) %>%    
  openxlsx::write.xlsx(., "yourfile.xlsx")                                             

# as csv
students_with_email_number %>% 
  select(name, draw_order) %>%    
  readr::write_csv(., "yourfile.csv")
```

