---
# title: Curriculum vitae Tormod Bøe
# name: Curriculum vitae with track record 
# surname: Bøe  
# position: "Associate Professor"
# qualifications: BPsych(Hons), Cand. Psychol, PhD
# address: "Institute of psychosocial science, \\tabularnewline Faculty of Psychology, \\tabularnewline University of Bergen, Norway"
# phone: +47 55 58 91 85 / +47 988 64 792
# www: "tormodboe.netlify.com \\ tormodteaching.netlify.com"
# www: tormodteaching.netlify.com 
# email: "Tormod.Boe@uib.no"
dob: test
# docname: "Tormod Bøe"
headcolor: "000000"
# twitter: mariecurie
# github: mariecurie
# linkedin: mariecurie
# aboutme: "trst"
# date: "`r format(Sys.time(), '%B %Y')`"
output:
  vitae::hyndman:
    # template: hyndmantemplate.tex
    keep_tex: yes
    keep_md: yes
    # latex_engine: xelatex
mainfont: Calibri
sansfont: Calibri
csl: /Users/st06810/Dropbox/References/csl/jama.csl
fontsize: 11pt
linestretch: 1.15
geometry: "left=2cm,right=2cm,top=2cm,bottom=2cm"
classoption: a4paper
header_includes:
  - \ExecuteBibliographyOptions{useprefix=true}
  - renewcommand{\bibfont}{\normalfont\fontsize{10}{12.4}\sffamily}
  - \newcommand{\blarge}{\begin{LARGE}}
  - \newcommand{\elarge}{\end{LARGE}}
  - \usepackage{amsmath}
  - \usepackage{amssymb}
  - \usepackage{lastpage}
  # - \usepackage[page]{totalcount}
  # - \usepackage{fontspec}

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(vitae)
source("/Users/st06810/Dropbox/AkademiskCV/baretable.R")

id <- 'TMC38ZgAAAAJ'
tb <- scholar::get_profile(id)
p <- scholar::get_publications(id)

# work in progress - list top cited articles also add chapter and report
# to be used for track record below
# p

p %>% select(title, author, cites) %>% arrange(-cites) %>% knitr::kable()

#### must also fix page number of total pages  - this is not working, unsure where to fix, probably in latex document (hyndman)
# maybe also look at cv for nfr grant - add something from there?

```

\blarge

\textbf{Curriculum vitae with track record}

\elarge

\vspace*{1\baselineskip}

<!-- \({\large\textbf{Role in project:}}\) \(\quad\)Project manager \(\quad\) Work package leader \(\quad\) Project partner [ ]  FOR NFR FORMÅL--> 

# PERSONAL INFORMATION
<!-- make all # headers caps!  -->

```{r pinf, results = 'asis'}
tribble(
  ~Text, ~Year, ~Degree, ~Gender,
  "Family name, First name:", "Bøe, Tormod", "", "",
  "Date of birth: ", "07.09.1978", "Sex:", "Male",
  "Nationality:",  "Norwegian", "", "",
  "Researcher unique identifier(s):", "0000-0002-0968-7537", "", "",
  "URL for personal website:", "\\url{https://tormodboe.netlify.com}", "", "",
) %>%
  baretable()
  # detailed_entries(Degree, Year, Institution)
```


# EDUCATION

```{r employment, results = 'asis'}
tribble(
  ~Year, ~Institution,
  "2010--2013", "\\textbf{Ph.D.}, University of Bergen, Bergen, Norway",
  "2005--2010", "\\textbf{Cand. Psychol}, University of Bergen, Bergen, Norway",
  "2001--2005", "\\textbf{B.Psych. (Hons)}, University of Newcastle, Newcastle, Australia",
) %>%
  baretable()
  # detailed_entries(Degree, Year, Institution)
```
\vskip -.1 in

# POSITIONS

## Current Position

```{r work, results='asis'}
library(tibble)
tribble(
  ~ Year, ~ Institution,
  "2018--", "\\textbf{Associate Professor}, Faculty of Psychology, University of Bergen, Bergen, Norway",
  "2018--", "\\textbf{Senior Researcher} (20\\% position), Uni Research Health, Bergen Norway"
  # "2014--2018",    "\\textbf{Senior Researcher}, Uni Research Health, Bergen, Norway",
  # "2014--2017",    "\\textbf{Post doctor} (funded by Norwegian research council), Uni Research Health, Bergen, Norway",
  # "2016--2016",    "\\textbf{Associate Professor}  (20\\% position), Faculty of Psychology, University of Bergen, Bergen, Norway",
  # "2010--2014",    "\\textbf{PhD student}, Uni Research Health, Bergen, Norway",
  # "2011--2012",    "\\textbf{Lecturer} (20\\% position), BI Norwegian, Business School, Bergen, Norway",
  # "2010--2010",    "\\textbf{Clinical psychologist}, Biskopshavn Family Councelling, Bergen, Norway"
  # # "2014--2018", "Senior Researcher", "Uni Research Health, Bergen, Norway",
  # "2016--2016", "Associate Professor  (20% position)", "Faculty of Psychology, University of Bergen, Bergen, Norway",
  # "2010--2014", "PhD student", "Uni Research Health, Bergen, Norway",
  # "2011-2012", "Lecturer", "BI Norwegian, Business School, Bergen, Norway", 
  # "2010", "Clinical psychologist", "Biskopshavn Family Councelling, Bergen, Norway",
  # "2006--2010", "Research assistant", "Uni Research Health, Bergen, Norway",
  ) %>% 
   baretable()
  
```

## Previous positions held

```{r prev_work, results='asis'}
tribble(
  ~ Year, ~ Institution,
  # "2018--", "\\textbf{Associate Professor}, Faculty of Psychology, University of Bergen, Bergen, Norway",
  # "2018--", "\\textbf{Senior Researcher} (20\\% position), Uni Research Health, Bergen Norway",
  "2014--2018",    "\\textbf{Senior Researcher}, Uni Research Health, Bergen, Norway",
  "2014--2017",    "\\textbf{Post doctor} (funded by Norwegian Research Council), Uni Research Health, Bergen, Norway",
  "2016--2016",    "\\textbf{Associate Professor}  (20\\% position), Faculty of Psychology, University of Bergen, Bergen, Norway",
  "2010--2014",    "\\textbf{PhD student}, Uni Research Health, Bergen, Norway",
  "2011--2012",    "\\textbf{Assistant Professor} (20\\% position), BI Norwegian, Business School, Bergen, Norway",
  "2010--2010",    "\\textbf{Clinical psychologist}, Biskopshavn Family Councelling, Bergen, Norway"
  # "2014--2018", "Senior Researcher", "Uni Research Health, Bergen, Norway",
  # "2016--2016", "Associate Professor  (20% position)", "Faculty of Psychology, University of Bergen, Bergen, Norway",
  # "2010--2014", "PhD student", "Uni Research Health, Bergen, Norway",
  # "2011-2012", "Lecturer", "BI Norwegian, Business School, Bergen, Norway", 
  # "2010", "Clinical psychologist", "Biskopshavn Family Councelling, Bergen, Norway",
  # "2006--2010", "Research assistant", "Uni Research Health, Bergen, Norway",
  ) %>% 
   baretable()
  
```

# FELLOWSHIPS, AWARDS AND PRIZES

```{r awards, results='asis'}
tribble(
  ~ Year, ~ Institution,
"2020--",     "Norwegian Research Council, project funding (Work package leader)" ,
"2019--",     "Norwegian Research Council, project funding (Collaborator)" ,
"2019",       "Department of psychosocial science, Faculty of Psychology (Scholarship for students)" ,
"2019",       "L. Meltzer foundation (Travel grant)" ,
"2018",       "L. Meltzer foundation (Travel grant)" ,
"2017--",     "Extra foundation, project funding (Funding for Ph.D.) ",
"2017",       "L. Meltzer foundation (Travel grant)" ,
"2017",       "Uni Research (STEP-application grant for internal collaboration projects)" ,
"2013--2017", "Norwegian Research Council, project scholarship (Post doctor), " ,
"2011--2013", "L. Meltzer foundation (Travel grant)" ,
"2006--2009", "Regional centre for child and youth mental health and child welfare, Uni health (Summer scholarship)" ,
"2007",       "University of Bergen (Scholarship)" ,
"2006",       "The University of Newcastle, Australia (Faculty medal)" , 
"2005",       "The University of Newcastle, Australia (Basic Science in Psychology Prize)" , 
"2003--2004", "The University of Newcastle, Australia (Faculty Commendation List)" , 
"2002", 	    "The University of Newcastle, Australia (Wilhelm Wundt Prize in First Year Psychology)",
) %>% 
     baretable()

```

# MOBILITY

```{r mobility, results='asis'}
tribble(
  ~ Year, ~ Institution, 
  # "2019--" , paste0("[",proj,"]", "(",url,")"), "",
  "2005", "Honours Thesis, University of New South Wales, Australia"
  # "2001--2004", "Bachelor of Psychology, University of New South Wales, Australia"
) %>% 
    baretable()
```

# PROJECT MANAGEMENT EXPERIENCE

```{r project, results='asis'}
tribble(
  ~ Year, ~ Institution, 
  # "2019--" , paste0("[",proj,"]", "(",url,")"), "",
  "2020--", "Longtrends, Work package leader, Funder: Norwegian research council (NRC)",
  "2019--", "New patterns - safe upringing, Researcher, Funder: NRC",
  "2014--", "Linkage of youth@hordaland to national registries for education, Leader, Funder: NRC",
  "2014--", "Linkage of youth@hordaland to national registries for service use, Researcher, Funder: NRC",
  "2018--", "The road to independence, Researcher, Funder: Wøyen foundation",
  "2006--", "Bergen Child Study/youth@hordaland studien, Researcher, Funder: NRC and others",
  "2014--", "EBU project, Researcher, Funder: NRC",
  "2016--", "Project Perfect, Researcher, Funder: Extra foundation",
  "2014--2017",    "Social inequalities, educational attainment and mental health (UNGSES), Leader, Funder: NRC",
  "2016--2017",    "Survey of living conditions in Askøy and Sotra, Leader, Funder: Municpalities",
) %>% 
    baretable()
```


# SUPERVISION OF GRADUATE STUDENTS AND RESEARCH FELLOWS

```{r supervision, results='asis'}
tribble(~ Year, ~ Institution,
"2019--",   "PhD, Cand. psychol. A. Skandsen",
"2018--",   "PhD, Cand. psychol. Y. Moussavi",
"2017--submitted", "PhD, Cand. psychol. S. Nilsen",
"2020",            "Masters thesis, Stud. psychol C. Lysenstøen",
"2020",            "Masters thesis, Stud. psychols H.A. Ostojic, H.A.S. Sørdal \\& V.J.S Lie",
"2020",            "Masters thesis, Stud. psychols I.A. Nordbøe, \\& K. Gjone",
"2018",            "Masters thesis, G.R. Skjønberg, \\& T. Digervold",
"2016" ,           "Masters thesis, Stud. psychols K. Bush, M. Hugaas \\& I.B. Grødem",
"2016" ,           "Masters thesis, Stud. psychol S. Nilsen",
"2015" ,           "Masters thesis, Stud. psychols S., Øie  \\& L.M., Aarsheim"
) %>%
    baretable()
```

# TEACHING ACTIVITIES

```{r, echo = F, message=F, warning=F}
library(readxl)
library(dplyr)
formidling <- read_excel("/Users/st06810/Dropbox/AkademiskCV/Formidling_Tormod.xlsx", sheet = "Ark2")
saveRDS(formidling, "formidling.rds")
n_delt <- formidling %>% select("Antall deltagere") %>% colSums(.)
startår <- formidling %>% select(År) %>% min()
slutttår <- formidling %>% select(År) %>% max()

# formidling <- formidling %>% filter(År>2017)
# formidling %>% dplyr::select(Arrangement, Arrangør, Mnd) %>% knitr::kable()
```

```{r confpres, results='asis'}
tribble(
  ~ Year, ~ Institution,
"2018--",  "Community Psychology, Faculty of Psychology, University of Bergen", 
"2019",           "National Congress in Psychology, The Norwegian Psychology association" ,
"2019",           "National conference on growing up, The Norwegian Directorate for Children, Youth and Family Affairs" ,
"2018",           "National conference for community psychologists, National Competence Center for Mental Health" , 
"2018",           "SLT conference, Ministry of Justice and Public Security" , 
"2017",           "The Schizoprenia Days, Stavanger University Hospital" , 
"2017", 	        "12. Nordic Public Health conference, Danish Health Authority",
"2015", 	        "Seminar on Social inequalities, Norwegian Directorate of Health", 
) %>% 
     baretable()
```

# ORGANISATION OF MEETINGS

```{r scimeetings, results='asis'}
tribble(
  ~ Year, ~Institution,
  "2020", "Professionally responsible, Norwegian conference on Social and Community Psychology, Norway", 
"2017",  "Professionally responsible, RKBU Conference, 400 participants, Norway"
# "2019",  "The Norwegian Directorate for Children, Youth and Family Affairs ", "National conference on growing up" ,
# "2018",  "National competencecenter for mental health", "National conference for community psychologists" , 
# "2018",  "Ministry of Justice and Public Security", "SLT conference" , 
# "2017",  "Stavanger University Hospital", "The Schizoprenia Days" , 
# "2017", 	"Danish Health Authority", "12. Nordic Public Health conference",
# "2015", 	"Norwegian Directorate of Health", "Seminar on Social inequalities", 
) %>% 
   baretable()
```


# INSTITUTIONAL RESPONSIBILITIES

```{r institu, results='asis'}
tribble(
  ~ Year, ~Institution,
"2019--",  "Revision of psychology education (Rethos), Faculty of Psychology" ,
"2017--", "PhD theses advisor",
"2015--", "Masters theses advisor"
# "2019",  "The Norwegian Directorate for Children, Youth and Family Affairs ", "National conference on growing up" ,
# "2018",  "National competencecenter for mental health", "National conference for community psychologists" , 
# "2018",  "Ministry of Justice and Public Security", "SLT conference" , 
# "2017",  "Stavanger University Hospital", "The Schizoprenia Days" , 
# "2017", 	"Danish Health Authority", "12. Nordic Public Health conference",
# "2015", 	"Norwegian Directorate of Health", "Seminar on Social inequalities", 
) %>% 
   baretable()

```

# COMISSIONS OF TRUST

```{r trust, results='asis'}
tribble(
  ~ Year, ~ Institution,
"2015--2019",  "Expert panel on social inequalities of health, The Norwegian Directorate of Health" ,
"2017",  "Review panel member, The Netherlands Organisation for Heath Research and Develeopment" ,
# "2019",  "The Norwegian Directorate for Children, Youth and Family Affairs ", "National conference on growing up" ,
# "2018",  "National competencecenter for mental health", "National conference for community psychologists" , 
# "2018",  "Ministry of Justice and Public Security", "SLT conference" , 
# "2017",  "Stavanger University Hospital", "The Schizoprenia Days" , 
# "2017", 	"Danish Health Authority", "12. Nordic Public Health conference",
# "2015", 	"Norwegian Directorate of Health", "Seminar on Social inequalities", 
) %>% 
   baretable()

```

<!-- # Membership of academies/scientific societies -->
<!-- \vskip -.15 in -->

<!-- # Major collaborations -->
<!-- \vskip -.15 in -->

# Track record

<!-- 1.	The total number of publications during the career. -->
<!-- 2.	A list of up to ten publications in major national or international peer-reviewed multidisciplinary scientific journals and/or in the leading national or international peer-reviewed journals, peer-reviewed conferences proceedings and/or monographs of their respective research fields. Indicate, if possible, the number of citations (excluding self- citations). -->
<!-- 3.	Research monographs and any translations thereof (if applicable).  -->
<!-- 4.	Granted patent(s) (if applicable). -->
<!-- 5.	Examples of leadership/participation in industrial or public innovation or design and/or highlights from research or innovation with societal impact (if applicable). -->
<!-- 6.	Leadership of field work or research expeditions (if applicable).	 -->
<!-- 7.	Invited presentations to peer-reviewed national or international conferences and/or international advanced schools (if applicable). -->
<!-- 8.	Experiences from major research communication, dissemination or outreach activities and/or invited presentations in public conferences (if applicable). -->

```{r, echo=FALSE}
# library(RefManageR)
first_lastauthor <- bibliography_entries("/Users/st06810/Dropbox/AkademiskCV/tpubs_zot.bib") %>%
  filter(bibtype == "Article") %>% 
  select(author) %>% 
  as.data.frame(.)

auth_split <- separate(first_lastauthor, col = "author", into=c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10"), sep = "and", remove = FALSE, fill = "right")
auth_split2 <- auth_split[2:11]

lastValue <- function(x)   tail(x[!is.na(x)], 1)
firstValue <- function(x)   head(x[!is.na(x)], 1)

firstauthor <- as.data.frame(apply(auth_split2, 1, firstValue))
colnames(firstauthor) <- "first"
lastauthor <- as.data.frame(apply(auth_split, 1, lastValue))
colnames(lastauthor) <- "last"

n_firstauthor <- firstauthor %>% dplyr::filter(stringr::str_detect(first, "Bøe")) %>% count()
n_lastauthor <- lastauthor %>% dplyr::filter(stringr::str_detect(last, "Bøe")) %>% count()
```

- I have authored or co-authored a total of `r length(unique(p$pubid))` publications (journal articles, book chapters and reports). I am the first author of `r n_firstauthor` peer reviewed journal articles and the senior author on `r n_lastauthor`. My articles have been cited `r tb$total_cites` times, my _h_-index is `r tb$h_index` and my _i10_-index is `r tb$i10_index` [according to Google Scholar](https://scholar.google.com/citations?user=TMC38ZgAAAAJ&hl=en). _(Updated `r format(Sys.Date(), "%d.%m.%Y")`)_. 
- Selected publications: 
```{r trackrefs}
bibliography_entries("/Users/st06810/Dropbox/AkademiskCV/tpubs_zot.bib") %>%
  filter(!is.na(ids)) %>% 
  mutate(ids = as.numeric(ids)) %>% 
           arrange(ids) 
```
<!-- 2.	A list of up to ten publications in major national or international peer-reviewed multidisciplinary scientific journals and/or in the leading national or international peer-reviewed journals, peer-reviewed conferences proceedings and/or monographs of their respective research fields. Indicate, if possible, the number of citations (excluding self- citations). -->

- I am the sole author of a report on social inequalities in child mental health commissioned by the Norwegian Directorate of Health. 
<!-- 5.	Examples of leadership/participation in industrial or public innovation or design and/or highlights from research or innovation with societal impact (if applicable). -->
- My research has been featured in several national policy documents, such as the [Government Strategy document for Children living in poverty](https://www.regjeringen.no/en/dokumenter/children-living-in-poverty/id2410107/). It was also the foundation for the main focus of the Norwegian Psychology Association in 2016-2019.  
-	I have been invited to give `r length(formidling$Lopenr)` talks for more than `r format(round(n_delt,-2), big.mark = " ")` participants in the period from `r startår` to `r format(Sys.time(),"%Y")`. Among those were several keynote presentations at national and nordic conferences. [Further details are available on my teaching website:  tormodteaching.netlify.com](https://tormodteaching.netlify.com/appendd.html). 
- I have collaborated with journalists on many dissemination projects, one of the most successful being "[Historier om fattigdom [Stories of Poverty]](https://www.bt.no/emne/Historier_om_fattigdom)", a series of articles published in the Norwegian newspaper Bergens Tidende, which by January 6th. 2020 had been read more than 1.2 million times. 
- Additional supervison experience include several funded student scholarships and many student papers (one of which has been published). Further details available upon request. 

\newpage

# LIST OF PUBLICATIONS

## PhD thesis
```{r thesis}
# library(RefManageR)
bibliography_entries("/Users/st06810/Dropbox/AkademiskCV/tpubs_zot.bib") %>%
  filter(bibtype == "Thesis")
```

## Refereed research papers 
<!-- ## Refereed research papers (last five years) -->
```{r}
id <- 'TMC38ZgAAAAJ'
tb <- scholar::get_profile(id)
```

```{r articles}
bibliography_entries("/Users/st06810/Dropbox/AkademiskCV/tpubs_zot.bib") %>%
  filter(bibtype == "Article") %>%
  # filter(date>2013) %>%
  arrange(desc(date))
```

\vskip .1 in

## Books and book chapters
```{r books}
bibliography_entries("/Users/st06810/Dropbox/AkademiskCV/tpubs_zot.bib") %>%
  filter(bibtype == "InCollection") 
```

## Conference proceedings
```{r conference}
bibliography_entries("/Users/st06810/Dropbox/AkademiskCV/tpubs_zot.bib") %>%
  filter(bibtype == "InProceedings") %>%
  arrange(desc(date), surnames)

```

## Reports

```{r}
bibliography_entries("/Users/st06810/Dropbox/AkademiskCV/tpubs_zot.bib") %>%
  filter(bibtype == "Report")
```



